---
title: "Project Euler 4"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Project 4
A palindromic number reads the same both ways. The largest palindrome made from the product of two 2-digit numbers is 9009 = 91 × 99.

Find the largest palindrome made from the product of two 3-digit numbers.


### Notes

The largest is going to have six digits.  So will look like $ghiihg$

$abc \times def = ghiihg$

Hence
$cf \mod 10 = g$

And there will be other relationships, but these are more complicated.

Easier may be to count down the palindromic numbers starting from $999999$, and then trying to factorise.  When it 
can be   factored as the product of two 3-digit numbers then bingo.



```{Rcpp}
#include <Rcpp.h>
using namespace Rcpp;

// [[Rcpp::export]]
bool IsPalindrome( long  n) {
   long  original=n;
   long  reversed=0;
    // reversed integer is stored in variable 
    while( n!=0 ) {
        int remainder = n%10;  
        reversed = reversed*10 + remainder;
        n /= 10;
    }
    // palindrome if orignal and reversed are equal
    if (original == reversed) return true;
    return false;
} 

// [[Rcpp::export]]
int largestpalindrome(int min, int max) {
  int currmax=0;
  for (int i=max; i>=min;i--) {
    for (int i2=i;i2>=min;i2--) {
      long test=i*i2;

      if (IsPalindrome(test)) {
        if (test > currmax)
          currmax=test;
      }
      
    }
    if (i*i < currmax) break;
  }
    return currmax;  
}
```


```{r}
system.time(
a <- largestpalindrome(501, 999)
)
print(a)
```